\replaced{Towards an o}{O}pen-source landscape for 3D CSEM modelling

### 2021-02-08 manuscript/Manuscript.tex

%% 2. Discretization %%
One of the key insights we gained from this study is that creating appropriate meshes is a difficult and time-consuming task. While there now exist several open-source 3D CSEM codes the capability for automatic meshing lacks behind and currently remains a largely manual task requiring experience in the field. It is important to state that the chosen models favour structured meshes. The first two examples can easily and accurately be represented by regular meshes. Using, for instance, a dipping layer instead of three resistive cubes would turn it around and make the model more favourable for unstructured meshes. MR3D would be an ideal scenario for unstructured meshes, as it is based on also published irregular lithological horizons. Since the corresponding resistivity model, however, was defined on a regular grid, the FE codes were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem. We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes. Both cases show that automatic and adaptive meshing capabilities are needed, which will increase the flexibility of 3D CSEM modelling \added{\mbox{\citep{GJI.11.Schwarzbach,GJI.16.Key}}}. Such meshing codes should also take into account the physics of CSEM computation with its diffusive behaviour. It is also important to state that the unstructured mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and corresponding source lines.
\ymark{I added this last sentence. Let me know what you think, we can take it out again or adjust/modify it:}
\added{Also, creating FV meshes is much simpler than creating FE meshes. However, having a FE mesh yields a lot o flexibility with regards to interpolation and refinement and adaption, making it more powerful once created.}

>>>>

%% 2. Discretization %%
One of the key insights we gained from this study is that creating appropriate meshes is a difficult and time-consuming task. While there now exist several open-source 3D CSEM codes the capability for automatic meshing lacks behind and currently remains a largely manual task requiring experience in the field. It is important to state that the chosen models favour structured meshes. The first two examples can easily and accurately be represented by regular meshes. Using, for instance, a dipping layer instead of three resistive cubes would turn it around and make the model more favourable for unstructured meshes. MR3D would be an ideal scenario for unstructured meshes, \added{as they are best suited to represent the irregular geometry provided by the} \deleted{as it is based on also published irregular} lithological horizons. Since the corresponding resistivity model, however, was defined on a regular grid, the FE codes were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem. We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes. Both cases show that automatic and adaptive meshing capabilities are needed, which will increase the flexibility of 3D CSEM modelling \added{\mbox{\citep{GJI.11.Schwarzbach,GJI.16.Key}}}. Such meshing codes should also take into account the physics of CSEM computation with its diffusive behaviour. It is also important to state that the unstructured mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and corresponding source lines.
\ymark{I added this last sentence. Let me know what you think, we can take it out again or adjust/modify it:}
\added{Also, creating FV meshes is much simpler than creating FE meshes. However, having a FE mesh yields a lot o flexibility with regards to interpolation and refinement and adaption, making it more powerful once created.}
